comgen-outline

### 2017-06-08 paper/appendix-alternativeRSAmodels.Rmd
create alt models appendix; begin full posterior appendix

---
title             : "Communicating generalizations about categories, events, and causes"
shorttitle        : "Communicating generalizations"

author: 
  - name          : "Michael Henry Tessler"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
    email         : "mtessler@stanford.edu"
  - name          : "Noah D. Goodman"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"

header-includes:
  - \usepackage{tabularx}
  - \usepackage{multicol}
  - \usepackage{wrapfig}
  - \usepackage{caption}
  - \usepackage{booktabs}

author_note: >
  Enter author note here.

abstract: > 
    Generalizations are central to human understanding yet can be difficult to acquire through direct experience (e.g., learning that a plant is poisonous).
    Language provides simple ways to convey generalizations (e.g., *Birds fly.*), and the language of generalizations is ubiquitous in everyday discourse and child-directed speech.
    Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
    One major issue in formalizing *genericity* is that such language is extremely flexible in its usage. 
    Using a state-of-the-art probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context. 
    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about events (i.e., *habitual language*, e.g., *John runs*), causes (i.e., *causal language*, e.g., *The block makes the machine play music.*), and categories (i.e., *generic language*, e.g., *Birds fly*), and find that the model, and not simpler models, explains full spectra of endorsements of generalizations in language.
    The model suggests that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.

keywords          : "genericity, generalizations, generics, pragmatics, semantics, bayesian modeling"
wordcount         : "X"

bibliography      : ["generics.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

\newcommand{\denote}[1]{\mbox{ $[\![ #1 ]\!]$}}
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\definecolor{Red}{RGB}{255,0,0}
\definecolor{Green}{RGB}{10,200,100}
\definecolor{Blue}{RGB}{10,100,200}
<!-- \newcommand{\ndg}[1]{\textcolor{Green}{$[ndg: #1 ]$}} -->
<!-- \newcommand{\mht}[1]{\textcolor{Blue}{$[mht: #1 ]$}} -->
<!-- \newcommand{\red}[1]{\textcolor{Red}{$#1$}} -->

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
                      echo=FALSE, warning=FALSE, cache=F, message=FALSE, sanitize = T)

```

```{r include = FALSE}
library("papaja")
```

```{r libraries}
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
# library(tidyr)
# library(dplyr)
library(data.table)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
project.path <- "~/Documents/research/comgen-paper/"
options("scipen"=10) 
```

# Introduction

Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge for a cognitive agent.
We learn such *generalizations* early in life by observing instances and drawing inductive inferences [@Dewar2010].
Social learning---relying upon the human capacity to infer others' intentions---faciliates this process [@Csibra2009; @Tomasello1999; @Butler2012].
At around a child's first birthday, her mind gains access to a new, human-unique source of data: language.

<!-- give rise to the productivity of human thought and form of foundations of cultural knowledge. -->
<!-- They allow us to understand the complex world around us and dream up how possible future situations might unfold. -->
<!-- It's been suggested that were psychology to have *general laws* akin to Newtonian laws in physics, the first general law in psychology would be of generalizations [Shepard1987]. -->
<!-- Generalizations are central to human understanding.  -->
<!-- Even before birth, human and non-human animals alike gather statistical information and form generalizations to predict what will come next. -->
<!-- The human learner, perhaps uniquely in the animal kingdom, displays striking sensitivity to the intentional and pedagogical actions of others, leading to distinct and often stronger inferences from data than would otherwise be warranted from random observations. -->

Minimally, language helps foster generalization by bringing attention to non-obvious shared relations through the use of labeling [@Gelman1986; @Graham2004; @Markman1989].
But language also has the ability to refer to *generalization itself*.
At around the age of two and a half, children begin to understand that *generic language* (e.g., "Dogs bark") refers to kinds and conveys generalizations that extend beyond the here and now [@Cimpian2008].
Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008].
It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that generics are central to the growth of conceptual knowledge [#Gelman2004] 
Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@Gelman2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010].
It's plausible that cultural knowledge accumulates across generations through language's ability to talk about generalizations [@Henrich2015].

Computational models of learning formalize the inferences derived from observations, focusing on the question of how children and adults generalize from sparse data [@Tenenbaum2011]. 
They showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012].
Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000].
Probabilistic models have recently made progress in describing pragmatic language understanding in precise terms [@Frank2012; @Goodman2013; @Goodman2016], formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013].
These models of rational communication describe inferences one can draw from language about *particular* situations: utterances that convey information about a specific entity or event.
The language of generalizations --- statements that extend beyond the here-and-now --- has heretofore eluded precise formalization.

The major issue in formalizing generic language is determining what makes a generic statement true or false. 
When we hear *Dogs bark*, we may feel it's a universal statment as in *All* dogs bark.
We may then realize that, among others, exquisitely well-trained dogs do not bark, which means the generic should signal something weaker like *Most* dogs bark.
Indeed, many generic statements seem to have the quantificational force of *most*. 
But most mosquitos do not carry malaria, while the statement *Mosquitos carry malaria* is intuitively true.
So the generic must in some way be compatible with *some* (e.g., *some mosquitos carry malaria*).
But equating the generic with *some* is too lenient: Some robins are female, but saying *Robins are female* seems odd.
Perhaps properties that only apply to one gender are an exception, but *Robins lay eggs* is intuitively true, despite the property being very similarly distributed among the population of robins as being female.

Generic statements convey generalizations about categories, but there are other linguistic devices that look different but seem to similary convey generalization.
*Genericity* can be observed when talking about categories (e.g., *Dogs bark*), people in general (e.g., *You never know what will happen on a blind date*), specific people (e.g., *Martha swims after work*), or causal events (e.g., *Drinking moonshines makes you go blind*).
Though this diverse array of utterances all seem to convey something beyond the here and now, what exactly is common to each of them is not obvious. 
Without a formal way of describing generalizations in language, we do not yet know in what ways these large swaths of language are similar.

In this paper, we combine a probabilistic model of pragmatic reasoning with ideas from formal semantics to define the truth conditions of generalizations in language. 
By formalizing such a hypothesis in a probabilistic language understanding model, we derive predictions for endorsements of such statements by specifying relevant prior knowledge.
Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is causally related to the endorsement of generalizations in the ways predicted by our model.
<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
We do this in three domains: generalizations about categories, events, and causes. 
In each domain, we define a scale that corresponds to the relevant metric by which a learner should generalize. 
We show that in each domain, our general theoretical framework applies and predicts endorsements about generalizations conveyed in language, when simpler models would fail.

The rest of this paper is organized as follows. 
In Section 1, we describe the Bayesian framework for generalization and define the scales along which generalization is measured in different domains. 
In Section 2, we formalize the hypothesis that the core of meaning of a generalization is *simple but underspecified* and incorporate this uncertain semantics into a general framework for pragmatic language understanding -- the Rational Speech Act framework.

To test our model, we examine endorsements of generalizations in three domains: categories, events, and causes.
Our model makes predictions about how endorsements should vary according to (i) the listener's world knowledge prior and (ii) the speaker's intended message (or, belief distribution) that she seeks to communicate. 
In Section 3, we describe experiments the measure both (i) and (ii) and relate it to the endorsements of generalizations about categories, or *generic language*. 
In Section 4, we describe experiments that measure (i) and manipulate (ii) to predict endorsements of generalizations about events, or *habitual language*.
In Section 5, we describe experiments that manipulate both (i) and (ii) to predict endorsements of generalizations about causes, or *causal language*. 
Across all of our experimental settings, we find a very strong agreement of our model's predictions to human elicited endorsement (cumulative $r^2(N) = 0.XX$), where simpler models fall short.
In the final section of the paper, we discuss how our model begins the process of unifying the extant psychological, linguistic, and philosophical literature on *genericity*.
Our theory also opens up a number of new directions for understanding generic language and building models that learn and think like people.

<!-- ALTERNATIVE INTRO -->

<!-- Yet, generalizations can be hard to acquire. -->
<!-- Consider what it would take to learn that under certain conditions (e.g., when eaten raw) a plant is poisonous, while under other conditions (e.g., when processed appropriately) the plant is nutritious.  -->
<!-- This is a common ecological problem and historical examples suggest that humans are not particularly good at learning such generalizations [e.g., the Australian explorers case; @Henrich2015]. -->
<!-- In this domain, the relationship to be learned (i.e., between different ways of food processing and the poisonousness of the plant) is non-obvious and trial-and-error learning is costly (negative examples entail death). -->

<!-- Crucially, once acquired, such hard-won generalizations can be communicated among humans, something which other animals struggle to accomplish [cite tomasello apes something]. -->
<!-- Generalizable knowledge can be inferred through demonstration, or in pedagogical contexts when ostensive cues are present [@Csibra].  -->
<!-- By and large, however, language provides the most flexible and generative way to communicate generalizations.  -->

<!-- A generalization provides a relation between a category and a property: It tells us to predict that property of future instances of the category [@HumeTHN]. -->
<!-- Generalization can be described as a probability and inductive inference as a probabilistic model [@Tenenbaum2011]. -->
<!-- From a very young age, children make strong inductive inferences from their experience in a way consistent with the Bayesian probability calculus [@Dewar2010; @Gelman1986; @Markman1989]. -->

<!-- If generalizations can be described by predictive probabilities, it would stand to reason that the most direct way to communicate a generalization would be to convey probability.  -->
<!-- Ironically, humans are very bad at describing and interpreting probabilities explicitly [@Tversky1974]. -->
<!-- Rather than be a deficiency, however, the difficulty we have in understanding numerical descriptions of probability might reflect the flexible adaptivity of natural language to make vague or ambiguous that which shared context can be relied upon to guide interpretation [@Piantadosi2012]. -->
<!-- If language has evolved in a way to make efficient the kinds of inductive inferences that are central to human cognition, we would expect the language of generalizations to be simple [c.f., @Leslie2008]. -->

<!-- Indeed, generalizations in language (e.g., *Dogs are friendly*, *Mary smokes cigarettes*, *Yeast makes bread rise*) are among the simplest forms of compositional expressions.  -->
<!-- Generalizations do not come in just one syntactic form: "*Dogs* are friendly", "*A library book* should be treated with respect", "*The contemporary foodie* seeks culinary experinces in menu-less restaurants and grandmothers' kitchens" [@Carlson1995; @NickelBlackwell; @sepGenerics]. -->
<!-- Each of these statements has in common the fact that they predicate a property of a category and the properties themselves apply to instances of the category (unlike, e.g., *Dinosaurs are extinct* because being extinct is not a property that can be true of a particular dinosaur).  -->
<!-- In this way, these statements exhibit *genericity*, or put another way, they convey generalizations. -->

<!-- In this paper, we formalize the language of generalizations with the interest is deciding what makes a generalization in language *true or false*. -->
<!-- How speakers convey generalizations and how listeners interpret them. -->

<!-- We examine three case studies of generalizations in language: Generalizations about agents, objects, and events.  -->
<!-- In Section 1, we introduce an information-theoric communicative theory of how generalizations are conveyed in language and flesh out the model's predictions alongside alternative models. -->
<!-- In order to do so, we provide a unified mathematical framework for dealing with agents, objects, and events, casting each as a category over which generalization can occur. -->
<!-- Our model predicts the endorsements of generalizations should vary with the (A) the probability of an instances having the property and (B) the prior distribution over the property probability (e.g., how likely instances of other categories are to have the property). -->
<!-- In Section 2, we introduce our empirical paradigm which we use to measure endorsement and interpretation of linguisitic generalizations, examining generalizations about *agents* in what is known as *habitual language* (e.g., "Mary smokes cigarettes.").  -->
<!-- In Section 3, we extend our paradigm to generalizations about *events* (i.e., *causal language* e.g., "Yeast makes bread rise.") and experimentally manipulate participants' background knowledge, showing that prior beliefs about probabilities are causally related to endorsement and interpretation of generalizations. -->
<!-- In Section 4, we use our paradigm to address long-standing theoretical and empirical puzzles regarding generalizations about *objects*, so-called *generic language*.  -->
<!-- We show our how model explains three known psychological puzzles surrounding generic language.  -->
<!-- In all case studies, we provide formal comparison to simpler models and in all cases, find that only our communicative theory explains the patterns of empirical data. -->
<!-- We conclude with a general discussion about the relationship of our theory to extant theories in the psychology, linguistics, and philosophy of genericity, and highlight the implications for modeling language acquisition, conceptual development, and other avenues of research that this framework opens. -->

<!-- the truth conditions of generalizations of events (so called *habitual language*) by manipulating the target propensity (A) while surveying a wide variety of events (which should induce variability in B). -->
<!-- In Section 3, we manipulate both (A) and (B) while testing the model on generalizations about causes (*causal language*). -->
<!-- If our theory is truly a theory about communicating generalizations, it should be able to explain the known psychological puzzles surrounding *generic language* (generalizations about categories).  -->

<!-- In stark constrast, a computational understanding of communicating generalizations is not well understood at all.  -->

<!-- Gathering data and observing evidence, however, is costly.  -->
<!-- The human problem of induction even displays a complex sensitivity to not only the type of data, but how the data was generated [@Gweon2010; @Shafto2012]. -->
<!-- A learner cannot form all of her abstract knowledge through direct experience, however. -->
<!-- Life is only so long, and you can only be in one place at a time. -->

<!-- In this paper, we introduce a formal model for understanding the language of generalizations. -->
<!-- <!-- The fact that generalizations in language seem to convey something about the propensity but that there seem to be as many interpretations of generalized statements as there are generalizations have confounded formal models aimed to capture their meaning. --> -->
<!-- We take as a starting point the idea that the core meaning of a linguistic generalization is simple (i.e., it conveys something about the propensity), but underspecified (i.e., there is uncertainty in the meaning). -->
<!-- We extend a rational model of communication --- the Rational Speech Act theory --- to be able to understand general statements that extend beyond the here-and-now. -->
<!-- We provide a number of stringest tests of this theory to explain generalizations about categories, events, and causal forces.  -->

<!-- How can generalizations in language have such flexible truth conditions while simultaneously carrying intuitive and, at times, very strong implications? -->
<!-- This question has been investigated by psychologists, linguists, and philosophers since @Carlson1977. -->
<!-- Here, we provide a unified formal theory of generalizations conveyed in language. -->
<!-- We test theory on the preeminent case study of linguistic generalizations: generic language, or generalizations about categories. -->
<!--  -->
<!-- To be precise, we develop a computational model that describes pragmatic reasoning about the propensity required to assert the generaization.   -->
<!-- We find that this formalism resolves known philosophical and empirical puzzles. -->
<!--We also provide the first set of experimental results about linguistic generalizations about events and causal forces, so called *habitual* and *causal statements*.-->

<!-- and find extreme flexibility in usage, which our model predicts.  -->

<!-- In Section 2, we conduct a set of experiments to test the *truth conditions* of familiar generalizations about categories (generic statements), and find our model predicts key patterns in human judgments -->
<!-- In Section 3, we conduct a set of experiments to test *interpretations* of novel generic sentences, again finding our model predicts human judgments with high quantitative accuracy. -->
<!-- In Section 4, we begin to test the generality of the theory, examining the *truth conditions* of generalizations about events. -->
<!-- In Section 5, we further probe our theory's generality, investing the *truth conditions* and *interpretations* of novel generalizations about causal forces.  -->
<!-- In all cases, we provide formal comparison to simpler models and in all cases, find that only our communicative theory with an underspecified meaning function explains the pattern of human data. -->
<!-- We also find that the prior beliefs used in our model reflect conceptual structure, and this provides an understanding of the conceptual implications of generics. -->
<!-- Finally, we investigate the underlying semantic scale in more detail, and find that the core meaning of generalizations in language depends in a crucial way on subjective beliefs, not mere frequency. -->

<!--
Most would agree that \emph{Swans are white}, but certainly not every swan is.
This type of utterance conveys a generalization about a category (i.e. \textsc{swans}) and is known as a generic utterance [@Carlson1977; @Leslie2008].
Communicating generically about categories is useful because categories themselves are unobservable [@Markman1989].
Knowledge about categories, while central to human reasoning, is tricky to acquire because categories themselves are unobservable [Markman1989}.
It is believed that every language can express generic meaning [@Behrens2005; @Carlson1995], and that generics are essential to the growth of conceptual knowledge [@Gelman2004] and how kinds are represented in the mind [@Leslie2008].
Generic language is ubiquitous in everyday conversation as well as in child-directed speech [@Gelman2008], and children as young as two or three understand that generics refer to categories and support generalization [@Cimpian2008].
and though English and many other languages do not possess an unambiguous form devoted to generic meaning [@Behrens2000, @AlMalki2014].
Additionally, generics are the primary way by which speakers discuss social categories, making them key to propagating stereotypes [@GelmanEtAl2004; @Rhodes2012; @Leslie2015] and impacting motivation [@Cimpian2010motivation].
Despite their psychological centrality, apparent simplicity, and ubiquity, a formal account of generic meaning remains elusive.

How can generics have such flexible truth conditions while simultaneously carrying strong implications?
In this paper, we explore the idea that the core meaning of a generic statement is simple, but underspecified, and that general principles of communication may be used to resolve precise meaning in context. 
In particular, we develop a mathematical model that describes pragmatic reasoning about the degree of prevalence required to assert the generic.  
We find that this formalism resolves the philosophical and empirical puzzles.
-->

# The Bayesian Framework for Generalizations

Generalizations are used to make predictions about instances that an agent has yet to experience [@HumeTHN].
From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993].
To form a generalization about a category or kind $k$, an observer must be able to individuate an exemplar or instance $x$ as belonging to the category.
The linguistic expression of such an individuation would manifest in utterances such as "$x$ is a $k$" or "this $k$ ..."
To generalize a feature $f$ to that category, it is also necessary to be able to determine if the particular instance has the feature.
That is, a speaker must be able to say "This $k$ (i.e., $x$) has $f$".
We call this kind of statement a *particular*.

```{r table-generalization, results="asis"}
df.tab <- data.frame(
  Generalization = c("Dogs are friendly", "John smokes", "Drinking moonshine makes you go blind"),
  #x = c("an instance of K in space", "an instance of K in time", "an instance of a "),
  "Generalization over" = c("Category", "Event", "Cause"),
  "Linguistic construct" = c("Generic", "Habitual", "Causal"),
  x = c("a dog", "an instance of John", "an instance of a person drinking moonshine"),
  k = c("DOGS", "JOHN", "DRINKING MOONSHINE"),
  f = c("is friendly", "is smoking / smoked at time t", "caused person to go blind")
) #%>% xtable(., 
 #        caption = c("Decomposition of generalizations into concrete particulars and corresponding properties."),
  #       label = c("tab:genpart"))

apa_table(df.tab, 
          caption = "Decomposition of generalizations into concrete particulars and corresponding properties.", 
          escape = TRUE, small = TRUE
)

#print(df.tab,  type = "latex", tabular.environment = "tabularx", width = "\\textwidth",  include.rownames = FALSE, comment = F)
```

We can make particular statements about objects, events, and causes.
We can say "My dog is friendly.", "John ran this afternoon.", or "My grandfather drank moonshine and it made him go blind."
To consider the corresponding generalizations (i.e., "Dogs are friendly", "John runs", "Drinking moonshines makes you go blind"), we must say exactly how the particular relates to the generalization.
We consider the generalization to be about a *category* and the particular to correspond to *instances* of that category.
Thus, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tabgenPart}).

Suppose we observe instances $\{x_1, x_2, ..., x_n\}$ of category $k$ and some number of them have feature $f$: What do we learn about possible future instances of $x_{n+1}$, particularly with respect to $f$?
For properties among instances of a category, we can describe an inductive inference by a probability $h$ $h = P(x \in f \mid x \in k)$^[
With a frequentist interpretation, this can be thought of as the *prevalence* of $f$ among $k$.
].
In the study of categories and properties, $x$ is an object.
For a behavior exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability integral: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$
In this case, $x$ is a instance of an agent.
Causal learning can be described with the same formalism as for categories, a probability referring to the probability of an effect $e$ given a cause $c$: $h = P(x \in e \mid x \in c)$.
We refer to this probability as $h$ because it represents a hypothesis about the underlying causal power or frequency that generated the observed data.
<!-- A Bayesian agent will have prior beliefs about the probability (potentially an uninformed prior) and uses Bayesian inference to learn about the probability from her observations. -->

<!-- Suppose *a priori* we have no informative beliefs about the propensity (i.e., $P(x \in f \mid x \in k) \sim \text{Uniform}(0, 1)$). -->
Observing some number of positive instances of $k$ with $f$ will update a prior belief distribution into a posterior belief distribution.
As a concrete example, consider the feature *is friendly* ($f$) for the category *dog* ($k$): $h = P(x \in \{\text{is friendly}\} \mid x \in \{\text{is a dog}\})$.
If an agent were to encounter some number of individual dogs, note how many of them were friendly ($d$), she could form a posterior belief distribution about the friendliness of dogs.

$$
P(h \mid d) = \frac{P(d \mid h) \cdot P(h)}{\int_{h'}P(d \mid h') \cdot P(h')}
$$

Our ability to use this updated belief $P(h \mid d)$ in order to make predictions about unobserved instances is a computational description of generalization [e.g., @Tenenbaum2006; @Tenenbaum2011].

The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
Inductive inferences show complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
Confounded causal evidence can be suddenly become unconfounded when you know the evidence was generated by an intentional agent [@Goodman2009].
Quantitative modeling has been crucial in explaining how the subtleties of experience relate to subtleties in generalization [@Tenenbaum2006; @Kemp2008].

Studying generalizations from observational evidence can only take us so far in understanding how the mind understands the world or culture accumulates across generations.
Relying upon observations would be particularly problematic to learn, for example, about properties that are difficult to observe (e.g., *cows have four stomachs*) or events that are statistically unlikely (e.g., *lightning strikes tall objects*).
For abstract, generalizable knowledge to remain in a culture, it must be able to be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.

# Communicating Generalizations with a Formal Model

We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the formalization described in the previous section. 
Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable of an individual (i.e., "My dog is friendly"). 
Bare plural statements (e.g., *Dogs are friendly*) strongly tend to yield a generic meaning, though other forms can express such a meaning [e.g., *A mongoose eats snakes.*; @Carlson1977] .

Given that generics express a property that can be applied to individuals, it seems intuitive that what makes the statement true or false would correspond to the number of individuals who hold the property.
At first glance, generics convey that *most* have the property, such as *Most dogs are friendly*.
*Robins lay eggs* is true, though, despite the fact that only female robins lay eggs (not exactly *most robins*). 
If generic statements can be true by restricting themselves to only be describing females, why does *Robins are female* seem like a weird statement to make?
Finally, *Mosquitos carry malaria* is intuitively true despite malaria only being present in a tiny fraction of a percentage of mosquitos.
It seems that any hard condition on the prevalence of the feature in the category (e.g., how many robins lay eggs) would violate intuitions.

These observations have led to proposals that prevalence or probability is only peripherally related to generic meaning. 
Conceptual accounts of generics emphasize the structure of generic knowledge [@Prasada2000], and view generic utterances as the way of expressing special mental relationships between kinds and properties [@Leslie2008; @Prasada2012]. 
From this perspective, the statement *Bishops move diagonally* is true not because most bishops move diagonally, but rather those are the rules of chess.
The most influential account in psychology is credited to @Leslie2007, who proposes that generics express a cognitively primitive, *default generalization*.

The *generics as default* view capitalizes on general cognitive principles to explain why certain generics are true or not.
*Mosquitos carry malaria* conveys a dangerous or striking property, which is useful to know about if you are trying to survive in a dangerous world.
This theory thus predicted that generics that convey striking properties would be true even if they were relatively rare (e.g., *Sharks attack swimmers*), which has been empirically verified [@Cimpian2010; @Prasada2013].
Other generics convey properties that are *characteristic* of a kind, such as *Robins lay eggs*, argued to have a *principled connection* between kind and property [@Prasada2006; @Prasada2013].

Yet, generics are not limited to conveying rich relations. 
Arbitrary relations can also be expressed like *Barns are red* or *Ravens are bigger than toasters*, which seem only to be true because of the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
The *generics as default* view must then be supplemented with the principle that, in certain situations, the statistics can influence generic endorsement.
How do we make sense of this panoply of conditions?
Is there some more general, unified principle that explains what makes generic statements true or false?

Bayesian cognitive models are used to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodman2015Chapter].
The basic currency of inference in these models is probability.
In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability.
If that's true, a simple, semantic theory (e.g., a threshold on subjective probability) may be enough to formalize the core meaning of a generic statement.

\begin{eqnarray}
L(h \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h)} \label{eq:L0fixed}
\end{eqnarray}

Equation \ref{eq:L0fixed} is a model of a listener $L$ who updates her beliefs $h$ according the meaning an utterance $u$.
$P(h)$ represents the listener's prior world knowledge concerning the relevant probabilities $h$.
The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenbaum2006; @Kemp2008].
We term this prior distribution the *prevalence prior*.
$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule, representing the literal semantics of utterances.
For an utterance conveying a generalization $u_{gen}$, we adopt a simple threshold semantics:

\begin{eqnarray}
\delta_{\denote{u_{gen}}(h, \theta)} & = & P(u_{gen} \mid h, \theta) \\
&\propto  &
\begin{cases}
1 & \text{if } h > \theta \\
0 & \text{otherwise}
\end{cases}
\end{eqnarray}

The $\delta_{\denote{u}(h, \theta)}$ likelihood is the Kronecker delta function returning $1$ for states $h$ greater than threshold $\theta$ and $0$ otherwise. 
Logical quantifiers can be described using threshold semantics (i.e., *some* is $h > 0$, all is $h = 1$).
What threshold $\theta$ should be used for the generic generalization?
We posit that meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener must infer $\theta$ in context.
In the probabilistic model, this is formalized as a prior distribution over the value of $\theta$.
We assume this prior is uninformed: $\theta \sim \text{Uniform}(0, 1)$.

\begin{eqnarray}
L(h, \theta \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h) \cdot P(\theta)} \label{eq:L0}
\end{eqnarray}

This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (a threshold function) but underspecified.
Figure \ref{fig:simulations} shows model $L$'s posterior distribution on $h$ upon hearing utterances corresponding to the uncertain threhsold (Eq. \ref{eq:L0}) as well as a comparison model using a fixed threshold at 0 (intuitively, corresponding to the quantifier "some").
The differences in the semantics are easily seen when considering a uniform distribution over $h$ (top left facet).
"Some" rules out only the lowest possible state and returns a posterior very similar to the prior.
The behavior of the generalization is distinct: The higher the $h$, the more likely the state is.

The intuition behind this behavior can be gleaned by imagining what the $L$ listener would believe with different thresholds and averaging over those possibilities.
If the threshold is very high, only the highest $h$ would pass the threshold.
If the threshold is slightly lower but still high, the highest $h$ probabilities would still pass the threshold, as would some that are slightly lower.
As the threshold takes on lower and lower values, more and more probabilities would surpass it.
When the threshold is very low, almost all probabilities are consistent with it (akin to "Some").
When the listener averages over these thresholds, higher values of $h$ pass more thresholds; thus, higher $h$ are more likely *a posteriori*.

In this paper, we are interested in explaining the variable endorsements of generalizations based on some known or believed probability $h$.
Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe an endorsement model as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq. \ref{eq:L0}).
\begin{equation} 
S(u \mid h) \propto \exp{(\lambda \cdot \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta  }
\label{eq:S1}
\end{equation}

In RSA, language production and comprehension are defined by recursive Bayesian models describing speaker and listener.
Following RSA, this speaker is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$.
The speaker's decision to say an utterance (e.g., the generalization) is determined with respect to how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
To model generic endorsement, this decision is evaluated in comparison to the alternative of *not saying the generalization*;
with just two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments [@Degen2014]. 
Formally, we consider the negative alternative as the option of staying quiet, which carries no information content^[
This alternative can be realized in at least two other ways: the speaker could have said the negation of the utterance (i.e., *The generalization is not true.*) or the negative generalization (i.e., *The opposite is true.*, e.g., *Ks do not have F*).
All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
]:

\begin{equation*}
\delta_{\denote{u_{silence}}(h, \theta)} \propto \begin{cases}
1 &\text{for all h}\ 
\end{cases}
\end{equation*}

Since the speaker $S$ doesn't know the threshold $\theta$, he must integrate over the likely values that the listener will infer. ^[
A more general version of this model can relax the assumption that the speaker has access to a degree of propensity $h$ that he is trying to communicate.
Rather, the speaker may have a belief distribution over $h$, corresponding to his beliefs about the rate with which an event happens or the prevalence of the property in the kind. 
In this situation, we would define the utility function to be the expected value of the informativity, which integrates over his belief distribution: 
$U(u; k) = {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(h, \theta \mid u)}  \diff \theta$
]

<!-- This decision is based on whether or not the generalization would accurately convey the $h$ -->
<!-- For addressing the question of whether or not a generalization is "true" or "felicitous", we consider how a Gricean speaker would act, given the goal of being informative to the literal listener (Eq. \ref{eq:L0}).  -->

<!-- S_{1}(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L_0(x, \theta \mid u)}  \diff \theta ) } -->

>>>>

# Appendix A: Alternative Rational Speech Act (RSA) models

The pair of speaker-listener models presented in the main text correspond to the simplest possible communicative models with an underspecified threshold meaning for a generalization. 
The Rational Speech Act framework defines a class of models with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).

Note that for the for the intial, simplest formulation of an RSA model, the level of recursion for a model can be unidentifiable from the 
"speaker optimality" model parameter in Eq. \ref{eq:S1} [@FrankEtAlUnderReview].
For our model, however, with an uncertain threshold variable, theoretically meaningful different models can be formulated in the pragmatic framework.

For example, @Lassiter2013 modeled vagueness and the context-sensitivity of gradable adjectives using a similar underspecified threshold semantics. 
In that work, the authors argued that understanding adjectives required a "pragmatic listener" [i.e., a listener who thinks about a speaker who thinks about a listener; @Lassiter2015]. 
In their model, the threshold variable was "pragmatically lifted": The uncertainty over the threshold variable was resolved using pragmatic reasoning [a so-called uRSA model; @Goodman2016].
In the case of our model of generalizations, we can compare the simple model we described above to a more sophisticated model that resolves the threshold using pragmatic principles.

## Listener models
